%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Jordan Ell} % Your name
\address{1156 Colville Rd Apt-204 \\ Victoria, British Columbia, Canada} % Your address
\address{(250)~$\cdot$~415~$\cdot$~9542 \\ jordan.ell7@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Victoria} \hfill {\em June 2013} \\
B.S. in Computer Science with Software Engineering \\
Jamie Cassels Undergraduate Research Scholarship (2012) \\
Presidents Scholarship (2008, 2012) \\
Graduating GPA: 7.73 (3.9)

{\bf University of Victoria} \hfill {\em June 2014} \\
MSc in Computer Science\\
UVic PHD Fellowship Awarded (2014)\\
GPA: 8.0 (4.0)

\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Ruboss}{June 2014 - Present}{Software Developer}{Victoria, BC}
\item Developer of Leanpub.com eBook eCommerce and writing website.
\item Technical lead for conversion of 2 rails applications to be rails and ReactJS.
\item Creation of development operations build and deployment systems for 3 applications.
\item Technologies used: Ruby, Ruby on Rails, JavaScript, ReactJS, node.js, Ansible.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Latitude Geographics}{May 2014 - June 2014}{Software Developer}{Victoria, BC}
\item Developing an industrial mapping tool on the standard web stack.
\item Creation of geolocation feature set.
\item Technologies used: TypeScript, JavaScript.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Riipen}{December 2013 - February 2015}{CIO / Software Developer}{Victoria, BC}
\item Developing the website Riipen.com to help students complete projects for employers.
\item Creation of REST API back end for 2.0 launch of the website.
\item Creation of front end web components using ReactJS.
\item Technologies used: Ruby, Ruby on Rails, CoffeeScript, ReactJS.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Victoria}{May 2012 - May 2014}{Software Engineering Researcher}{Victoria, BC}
\item Researching in the realm of indirect software conflicts.
\item Creation of bug prediction and prevention tools.
\item Creation of natural language processing tools for requirement elicitation and sentiment analysis.
\item Technologies used: Java, Ruby, Ruby on Rails, JavaScript, HTML, CSS, PostgreSQL.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IBM}{September 2010 - April 2011}{Environment Support}{Vancouver, BC}
\item Orchestrated the deployment and maintenance of Linux, Windows, and AIX, project servers.
\item Creation of a single sign on authentication system across Unix and Linux platforms.
\item Creation of an OS and middle ware patch management system to track required and applied software patches.
\item Creation of self correcting backup systems to complete backup cycles.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{James Evans and Associates}{May 2010 - September 2010}{Software Developer}{Victoria, BC}
\item Developed Oracle Forms as a front end for pension management systems.
\item Created and managed large SQL scripts / libraries for maintaining sets of data in a Oracle database.
\item Technologies used: Oracle Database, Oracle Forms, C++.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

{\bf Identifying failure inducing developer pairs within developer networks} \hfill {\em2013} \\
ICSE '13 Proceedings of the 2013 International Conference on Software Engineering Pages 1471-1473 \\
Authors: Jordan Ell \\
ISBN: 978-1-4673-3076-3

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

GitHub at: github.com/jordanell

\begin{rSubsection}{AtomVote.com}{August 2015 - September 2015}{Software Developer}{}
\item Creation of the website AtomVote.com which is a simple polling platform.
\item `AtomVote` is available for web use, has a JSON API, and integrates with Slack.
\item Technologies used: Ruby on Rails, ReactJS, PostgreSQL.
\end{rSubsection}

\begin{rSubsection}{Block3r}{December 2013 - February 2014}{Software Developer}{}
\item Creation of the game ``Block3r'' for Windows Phone.
\item ``Block3r'' has over 10K downloads, with an average rating of 3.5 stars.
\item Technologies used: C\#, Microsoft GameStudio 4.0.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Software Languages & Ruby, JavaScript/CoffeeScript, C\#, Java, Python \\
Frameworks & Ruby on Rails, ReactJS, node.js, .NET \\
Databases & PostgreSQL, MySQL, MongoDB \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% REFERENCES
%----------------------------------------------------------------------------------------

\begin{rSection}{References}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{12cm} }
Braden Simpson & CTO at Riipen, braden@riipen.com, 1-250-858-3628 \\
Scott Patten & CTO at Ruboss, scott@ruboss.com, 1-604-341-1701 \\
Mike Rowe & CEO at Accio, mike@myaccio.com, 250-217-2392
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}